Journal and article coverage

### 2025-02-19 analysis/manuscript.qmd
Use pdf figures in latex output

```{r, setup, echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  fig.width = 6,
  fig.asp = 0.618,
  out.width = "99%",
  fig.align = "center",
  dpi = 300,
  dev = c("png", "cairo_ps", "pdf"),
  fig.path = "fig/",
  fig.pos = "ht!", out.extra = ""
)
options(scipen = 999, digits = 2)
knitr::knit_hooks$set(
  inline = function(x) {
    if (is.numeric(x)) {
      return(prettyNum(x, big.mark = ","))
    } else{
      return(x)
    }
  }
)
```

>>>>

```{r, setup, echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  fig.width = 6,
  fig.asp = 0.618,
  out.width = "99%",
  fig.align = "center",
  dpi = 600,
  dev = c("pdf", "cairo_ps", "png"),
  fig.path = "fig/",
  fig.pos = "ht!", out.extra = ""
)
options(scipen = 999, digits = 2)
knitr::knit_hooks$set(
  inline = function(x) {
    if (is.numeric(x)) {
      return(prettyNum(x, big.mark = ","))
    } else{
      return(x)
    }
  }
)
```

### 2025-02-19 analysis/manuscript.tex
Use pdf figures in latex output

\includegraphics[width=0.99\linewidth,height=\textheight,keepaspectratio]{fig/fig-upset_coverage_results-1.png}

@@

\begin{center}
\includegraphics[width=0.99\linewidth,height=\textheight,keepaspectratio]{fig/upset_publisher_plot-1.png}
\end{center}

>>>>

\includegraphics[width=0.99\linewidth,height=\textheight,keepaspectratio]{fig/fig-upset_coverage_results-1.pdf}

@@

\begin{center}
\includegraphics[width=0.99\linewidth,height=\textheight,keepaspectratio]{fig/upset_publisher_plot-1.pdf}
\end{center}
